Verifying Demonstrations

### 2018-08-28 paper/adversary-model.tex
Brings adversary fig captions up-to-date

\begin{figure}
  \centering
  \includegraphics{base-identity-cause-adversary.tikz}
  \caption{\label{fig:identity-cause-adversary}%
    An overview of the base protester adversary model.
    The protester with real identity \(P\) and witness with real identity \(W\) 
    communicate and each learn only the protocol data, \(d_{P,W}(\cid, P)\), 
    and the time it happened, \(t_{P,W}\).
    The protester submit some function of the protocol data \(f(d_{P,W}(\cid, 
      P))\) to the storage \(S\), who learns only that and the time it 
    happened, \(t_{P,S}\).
    Both the witness \(W\) and storage \(S\) are controlled by the adversary 
    \(A\).
  }
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{base-identity-location-adversary.tikz}
  \caption{\label{fig:identity-location-adversary}%
    An overview of the base witness adversary model.
    The protester with real identity \(P\) and witness with real identity \(W\) 
    communicate and each learn only the protocol data, \(d_{P,W}(W, l)\), and 
    the time it happened, \(t_{P,W}\).
    The witness submit some function of the protocol data \(f(d_{P,W}(W))\) to 
    the storage \(S\), who learns only that and the time it happened, 
    \(t_{W,S}\).
    Both the protester \(P\) and storage \(S\) are controlled by the adversary 
    \(A\).
  }
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics{base-identity-cause-adversary.tikz}
  \caption{\label{fig:identity-cause-adversary}%
    An overview of the base identity--cause adversary model.
    The protester with real identity \(P\) and witness with real identity \(W\) 
    communicate and each learn only the protocol data, \(d_{P,W}(\cid, P)\), 
    and the time it happened, \(t_{P,W}\).
    The protester submits \(f(d_{P,W}(\cid, P))\), for some function \(f\), to 
    the storage \(S\), who learns only that and the time it happened, 
    \(t_{P,S}\).
    Both the witness \(W\) and storage \(S\) are controlled by the adversary 
    \(A\).
  }
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{base-identity-location-adversary.tikz}
  \caption{\label{fig:identity-location-adversary}%
    An overview of the base identity--location adversary model.
    The protester with real identity \(P\) and witness with real identity \(W\) 
    communicate and each learn only the protocol data, \(d_{P,W}(W, l)\), and 
    the time it happened, \(t_{P,W}\).
    The witness submits \(f(d_{P,W}(W))\), for some function \(f\), and the 
    protester submits \(g(d_{P,W}(P,l))\), for some function \(g\), to the 
    storage \(S\), who learns only that and the time it happened, \(t_{W,S}\) 
    respectively \(t_{P,S}\).
    Only the storage \(S\) is controlled by the adversary \(A\).
  }
\end{figure}
